Crowdy: Social Crowd Visualization

### 2011-03-29 docs/crowdy_gui.tex

\begin{figure*}[t]
\centering
\includegraphics[width=400pt]{img/UIdesign.eps}
\caption{Crowdy User Interface Design}
\label{fig:UIdesign}
\end{figure*}

@@

Identifying highly dynamic ad-hoc collections of users what we refer to as
crowds in massive social messaging systems like Twitter and Facebook is
important \cite{krishna:2010}. K. Y. Kamath et al. in the study suggest an
efficient locality-based clustering approach for identifying crowds of users in
near real-time compared to more heavyweight static clustering algorithm. The
study consisted of 711,612 users and 61.3 million messages, and tells what
approaches to follow to efficiently and effectively identify Twitter-based
crowds.

In the other study based on the previous one, K. Y. Kamath et al
\cite{krishna:2011}, they add another salient feature - a novel crowd tracking
and evolution approach for linking crowds across time periods. Unlike the more
static and long-lived group-based membership offered on many social networks
their goal was to support the discovery of organic and highly-temporal group
affiliation, which they refer to as ``transient crowds''. A transient crowd
according to them is a potentially short-lived ad-hoc collection of users bound
together by some common thread – which can be communication-based,
location-based or interest based. We are inspired by this idea of formation and
detection of crowds. We try to implement detection of crowd in Crowdy in a
similar fashion.

@@

\section{Implementation}
The system is designed to run in a user's web browser.  As a result, we decided
to use some fairly standard web tools to implement the system.  The system that
we are building the user interface on top of exposes a RESTful API.  Although
it is not a part of this project, it is important to understand how the backend
works, and how it fits into this project.  First, a crawler retrieves tweets
from Twitter using Twitter's REST API, search API, and streaming API.  Next,
this data goes through several filters that add additional information to the
users and tweets.  After that, a program finds groups of users based on their
communication patterns.  This data is stored as JSON in a MongoDB database.
The backend also provides the RESTful API that we connect to.  To retrieve
data, our system makes an HTTP GET request to the server.  The server returns
data in the JSON format, which is easy to decode in Javascript.  Our GUI never
directly reads from or writes to the database.

@@

The code that will run on the user's web browser has to be written in
Javascript.  We use the jQuery library to handle events, retrieve JSON, and
abstract away the idiosyncrasies of the various web browsers.  We are using the
Simile Timeline library to produce the crowd timelines.  In the future, we may
use the Google Maps API to display crowds on a map.

>>>>

\begin{figure*}[t]
\centering
\includegraphics[width=\linewidth]{img/UIdesign.jpg}
\caption{Crowdy User Interface Design}
\label{fig:UIdesign}
\end{figure*}

@@

Identifying highly dynamic ad-hoc collections of users what we refer to as
crowds in massive social messaging systems like Twitter and Facebook is
important \cite{krishna:2010}. Kamath et al. in the study suggest an
efficient locality-based clustering approach for identifying crowds of users in
near real-time compared to more heavyweight static clustering algorithm. The
study consisted of 711,612 users and 61.3 million messages, and tells what
approaches to follow to efficiently and effectively identify Twitter-based
crowds.

In the other study based on the previous one, Kamath et al
\cite{krishna:2011}, they add another salient feature - a novel crowd tracking
and evolution approach for linking crowds across time periods. Unlike the more
static and long-lived group-based membership offered on many social networks
their goal was to support the discovery of organic and highly-temporal group
affiliation, which they refer to as ``transient crowds''. A transient crowd
according to them is a potentially short-lived ad-hoc collection of users bound
together by some common thread – which can be communication-based,
location-based or interest based. We are inspired by this idea of formation and
detection of crowds. We try to implement detection of crowd in Crowdy in a
similar fashion.

@@

\section{Implementation}

\subsection{Workflows}

The system is designed to run in a user's web browser. As a result, we decided
to use some fairly standard web tools to implement the system. The system that
we are building the user interface on top of exposes a RESTful API. Although
it is not a part of this project, it is important to understand how the backend
works, and how it fits into this project. The workflows of the system can be
decomposed into following parts: (i) a crawler retrieves tweets from Twitter using
Twitter's REST API, search API, and streaming API; (ii) the corresponding data
go through several filters that add additional information to the users and
tweets; (iii) a program finds groups of users (i.e., crowds) based on their 
communication patterns; (iv) the data of crowds are stored as JSON in a MongoDB
database; (v) the backend also provides the RESTful API that we connect to; (vi)
to retrieve data, our system makes an HTTP GET request to the server, and the 
server returns data in the JSON format, which is easy to decode in Javascript.
To make the architecture clean, we never allow our GUI directly read from or 
write to the database.

\subsection{Techniques}

@@

The code that will run on the user's web browser has to be written in
Javascript. We use the jQuery library to handle events, retrieve JSON, and
abstract away the idiosyncrasies of the various web browsers. We are using the
Simile Timeline library \cite{simile} to produce the crowd timelines. In the 
future, we may use the Google Maps API to display crowds on a map.

\subsection{Features}

In the system, we provide three perspectives to visualize the crowds: (i) timeline;
(ii) list; (iii) map. We also support search function so users are able to search 
crowds given query of text, time period of crowd, and size of crowd, and visualize
the crowds with the three options of perspectives.

\subsubsection{Timeline}

We apply the Simile Timeline library which is developed by MIT's Computer Science
and Artificial Intelligence Laboratory. BLAHBLAH WAITING JEFF'S STUFF.

The timeline view

\subsubsection{List}

The list view requires a dynamic table in which it display as many rows as the
amount of crowds returned by the API. Concretely, we issue a jQuery for all the
available crowds in the database. The javascript helps to create the dynamic
table which includes the following columns: Period, Tweets, Users. Ideally,
this table should support sorting by column. Other than that, we plan to 
implement detail information box for the tweets and user column after a row 
is selected. In order to provide users a more clean page view, we may 
restrict 10 crowds per page and thus, a multiple page navigation is possible.

\subsubsection{Map}

\subsubsection{Search}

In the search function of the system, we provide a main search box in which 
users can type a textual query to search for crowds which contains the query.
Besides, users can also click the link of advanced search, so that they can 
choose options of words, time period of crowd, size of crowd, presentation ways,
and results they would like to see per page. We maintain indices for each kind
of queries in the MongoDB database, so that we can efficiently return the results
to users. Whenever a query is issued, the systems send a HTTP GET request to the
backend, and the server would return the corresponding search results.

In our future direction, we will also provide query options like location, user's
screen name. So that users can search crowds that are in a specific city or an 
area, and also search crowds that a specific user is involved in.
